---
title: "30 mai"
author: "Antoine"
date: \`r format(Sys.Date(), "%m %d,%Y")`\
output:
  slidy_presentation: default
---

```{r setup, include=FALSE}
rm(list=ls())

# packages
library(tidyverse)
library(DescTools)
library(tis)


# options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 13, fig.align = "center")
```

```{r multiplot function}

# multiplot function : several ggplot on the same page

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

```{r load data dyn.}
## wd
data_path <- "data/inf-rate-4"

## dyn
filename.dyn <- list.files(data_path, 
                           pattern="^tick-[0-9]{1,4}-[0-9]{1,2}-[0-9]{1,2}-[0-9]{1,2}.txt")

column.names.dyn <- c(
  # init.params
  "infection.rate",
  "proportion",
  "agregation",
  "proba.overwintering",
  "nb.init",
  "proba.birth",
  # time
  "year",
  "tick",
  # outputs
  "nb.visited.patches",
  "dyn.never.inf",
  "dyn.inf",
  "dyn.inf.non.occ",
  "dyn.inf.occ",
  "dyn.cured",
  "dyn.adults",
  "tot.inf.cur",
  "dyn.curation")

## load -> data.dyn contient toutes les données, y compris le control (nb.init 0 / proportion 0)

data.dyn <- tibble(filename.dyn) %>% 
  # load whole data
  mutate(file_contents = map(filename.dyn, ~ read_delim(file.path(data_path, .), delim = " ", col_names = column.names.dyn))) %>% 
  unnest()
```

# Traitement de plusieurs simulations

## Dyn. inf . : variabilité entre simulations

- Chaque config. : 10 simulations (1 couleur par simulation)
- Valeurs = nb. de patches avec statut infecté


```{r inf variance simul Y1 Y5}
plotY1 <- data.dyn %>% 
  # filter Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = dyn.inf, colour = filename.dyn)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  # on enlève la légende (illisible)
  guides(colour=FALSE)

plotY5 <- data.dyn %>% 
  # filter Y5
  filter(year == 5) %>%
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = dyn.inf, colour = filename.dyn)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  # on enlève la légende (illisible)
  guides(colour=FALSE)

multiplot(plotY1, plotY5, rows=2)
```

## Dyn. inf. : comparaisons entre mean et median : Year 1

- dyn. inf. = taux de remplissage (normalisé par le nb. de crop patches)
- mean / median sur les 10 simuls pour chaque config.

```{r inf comparison mean median Y1}

### mean

data.dyn.mean <- data.dyn %>% 
  # average dyn.inf : mean
  group_by(infection.rate, proportion, agregation, nb.init, year, tick) %>% 
  mutate(mean.inf = mean(dyn.inf)) %>% 
  distinct(infection.rate, proportion, agregation, nb.init, year, tick, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # classic data.dyn2
  # select data we are interested in
  select(- filename.dyn, - proba.birth, -proba.overwintering, - nb.visited.patches, - tot.inf.cur, - dyn.curation) %>%   
  # tot crop patches in the landscape
  mutate(stock.crops = 1089 - floor(1089*proportion/100)) %>% 
  # % of landscape infected : average dyn.inf -> mean.inf
  mutate(fill.level = mean.inf*100/stock.crops) %>%
  # numeric -> factor (for ggplot)
  mutate(infection.rate = factor(infection.rate)) %>% 
  mutate(proportion = factor(proportion))

plot.mean <- data.dyn.mean %>% 
  # Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = fill.level)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Mean 10 simulations Y1")

### median

data.dyn.median <- data.dyn %>% 
  # average dyn.inf : mean
  group_by(infection.rate, proportion, agregation, nb.init, year, tick) %>% 
  mutate(median.inf = median(dyn.inf)) %>% 
  distinct(infection.rate, proportion, agregation, nb.init, year, tick, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # classic data.dyn2
  # select data we are interested in
  select(- filename.dyn, - proba.birth, -proba.overwintering, - nb.visited.patches, - tot.inf.cur, - dyn.curation) %>%   
  # tot crop patches in the landscape
  mutate(stock.crops = 1089 - floor(1089*proportion/100)) %>% 
  # % of landscape infected : average dyn.inf -> mean.inf
  mutate(fill.level = median.inf*100/stock.crops) %>%
  # numeric -> factor (for ggplot)
  mutate(infection.rate = factor(infection.rate)) %>% 
  mutate(proportion = factor(proportion))

plot.median <- data.dyn.median %>% 
  # Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = fill.level)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Median 10 simulations Y1")

### multiplot comparison mean / median

multiplot(plot.mean, plot.median, rows=2)
```

## Dyn. inf. : comparaisons entre mean et median : Year 5

```{r inf comparison mean median Y5}

### mean

plot.mean <- data.dyn.mean %>% 
  # Y5
  filter(year == 5) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = fill.level)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Mean 10 simulations Y5")

### median

plot.median <- data.dyn.median %>% 
  # Y5
  filter(year == 5) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = fill.level)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Median 10 simulations Y5")

### multiplot comparison mean / median

multiplot(plot.mean, plot.median, rows=2)
```

## Dyn. pred. : variabilité entre simulations

- Chaque config. : 10 simulations (1 couleur par simulation)
- Valeurs = nb. de predators

```{r pred variance simul Y1 Y5}
plotY1 <- data.dyn %>% 
  # filter Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = dyn.adults, colour = filename.dyn)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  # on enlève la légende (illisible)
  guides(colour=FALSE)

plotY5 <- data.dyn %>% 
  # filter Y5
  filter(year == 5) %>%
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = dyn.adults, colour = filename.dyn)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  # on enlève la légende (illisible)
  guides(colour=FALSE)

multiplot(plotY1, plotY5, rows=2)
```


## Dyn. pred. : comparaisons entre mean et median : Year 1

- dyn. inf. = taux de remplissage (normalisé par le nb. de crop patches)
- mean / median sur les 10 simuls pour chaque config.

```{r pred comparison mean median Y1}

### mean

data.dyn.mean <- data.dyn %>% 
  # average dyn.adults : mean
  group_by(infection.rate, proportion, agregation, nb.init, year, tick) %>% 
  mutate(mean.adults = mean(dyn.adults)) %>% 
  distinct(infection.rate, proportion, agregation, nb.init, year, tick, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # numeric -> factor (for ggplot)
  mutate(infection.rate = factor(infection.rate)) %>% 
  mutate(proportion = factor(proportion))

plot.mean <- data.dyn.mean %>% 
  # Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = mean.adults)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Mean 10 simulations Y1")

### median

data.dyn.median <- data.dyn %>% 
  # average dyn.adults : mean
  group_by(infection.rate, proportion, agregation, nb.init, year, tick) %>% 
  mutate(median.adults = median(dyn.adults)) %>% 
  distinct(infection.rate, proportion, agregation, nb.init, year, tick, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # numeric -> factor (for ggplot)
  mutate(infection.rate = factor(infection.rate)) %>% 
  mutate(proportion = factor(proportion))

plot.median <- data.dyn.median %>% 
  # Y1
  filter(year == 1) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = median.adults)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Median 10 simulations Y1")

### multiplot comparison mean / median

multiplot(plot.mean, plot.median, rows=2)
```

## Dyn. pred. : comparaisons entre mean et median : Year 5

```{r pred comparison mean median Y5}

### mean

plot.mean <- data.dyn.mean %>% 
  # Y5
  filter(year == 5) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = mean.adults)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Mean 10 simulations Y5")

### median

plot.median <- data.dyn.median %>% 
  # Y5
  filter(year == 5) %>% 
  # filter
  filter(agregation == 5) %>% 
  filter(nb.init == 10) %>% 
  filter(infection.rate == 4) %>% 
  ggplot() +
  geom_point(aes(x = tick, y = median.adults)) +
  facet_grid(. ~ proportion, labeller = label_both) +
  ggtitle("Median 10 simulations Y5")

### multiplot comparison mean / median

multiplot(plot.mean, plot.median, rows=2)
```
